Abstract Data Type Inference

### 2015-03-21 histories.tex
Added possible history notation.

@@

  TODO HISTORY OF AN EXECUTION

>>>>

\begin{example}
  \label{ex:executions}

@@

  The histories of the Executions $e_1$, $e_2$, and $e_3$ of
  Example~\ref{ex:executions} are
  \begin{align*}
    & H(e_3) = \big( \underline{\mathrm{write}:1} \big) \big( \underline{\mathrm{write}:2} \big) \big( \mathrm{read}:1 \big) \\
    & H(e_2) = \big( \underline{\mathrm{write}:1} \parallel \underline{\mathrm{write}:2} \big) \big( \mathrm{read}:1 \big) \\
    & H(e_3) = \big( \underline{\mathrm{write}:1} \big) \big( \underline{\mathrm{write}:2} \parallel \mathrm{read}:1 \big)
  \end{align*}
  TODO IS THIS NOTATION GOOD ENOUGH?
